### 2015-05-10 paper.tex
Defining inner ring

\subsection{Algorithm}
First, like in the paper, we'll begin by briefly discussing the intuition of the algorithm.

@@

>>>>

\subsection{Algorithm}
First, like in the paper, we'll begin by briefly discussing the intuition of the $(1 + \epsilon)$ approximation algorithm.

@@

\subsubsection{Inner Ring}

Define a \emph{cheap cluster} as one where $OPT_i \leq \frac{\beta \epsilon OPT}{32}$, meaning it's less than $\frac{32}{\beta \epsilon}$ of $OPT$.  Let the \emph{inner ring} of $C_i$ be the set of points $x$ such that $d(x, c_i) \leq \frac{ \beta OPT }{8 |C_i|}$.  If $C_i$ is cheap, then no more than $\frac{\epsilon}{4}$ points reside outside its inner ring.  By contradiction, assume that more than $\frac{\epsilon}{4}$ fraction of points exist outside of the inner ring.  $OPT_i > (points outside inner ring) * (cost of points)$, and the first term in that product is lower bounded by $\frac{\epsilon |C_i|}{4}$ and that second term is lower bounded by $\frac{\beta OPT}{8 |C_i|}$.  Thus, $OPT_i > \frac{\beta \epsilon OPT }{32}$.  But all cheap clusters have cost less than $\frac{\beta \epsilon OPT}{32}$, so we have a contradiction, and thus cheap clusters only have at most $\frac{\epsilon}{4}$ points outside their inner rings.

TODO: what on Earth does Markov's inequality have to do with this?  Is this a typo in the paper?

\subsubsection{The Algorithm}

Blah blah blah describe algorithm here

\subsubsection{Bounds on Components of Cheap Clusters}
We now move into the proof of correctness, and start by proving a useful lemma here.  As mentioned before, our goal is to find lists of \emph{components}, or subsets of points, from which we hope we can derive our clusters.  We now show that, if we bound
